Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
修改 drop rate 为百分比

\begin{table}[t]
\centering
\scriptsize
\tabcolsep=2.0pt
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}ccc|cccc@{}}
\toprule
Method & Tracker & Backbone & \begin{tabular}[c]{@{}c@{}}Attack\\ Cost(ms)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Clean\\ Videos\end{tabular} & \begin{tabular}[c]{@{}c@{}}Perturbed\\ Videos\end{tabular} & \begin{tabular}[c]{@{}c@{}}Drop\\ Rate\end{tabular} \\ \midrule
CSA & SiamRPN & AlexNet & 4720 & 0.851 & 0.458 & 0.46 \\
FAN & SiamFC & AlexNet & 10 & 0.720 & 0.180 & 0.75 \\
TTP & SiamRPN++ & ResNet-50 & 8 & 0.910 & 0.080 & 0.91 \\
\midrule
Ours & SiamFC++ & GoogLeNet & 0 & 0.861 & 0.048 & 0.94 \\ \bottomrule
\end{tabular}%
%}
\caption{Precision score relative to the real trajectory on OTB2015.}
\label{tab:untargeted}
\end{table}

>>>>

\begin{table}[t]
\centering
\scriptsize
\tabcolsep=2.0pt
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}ccc|cccc@{}}
\toprule
Method & Tracker & Backbone & \begin{tabular}[c]{@{}c@{}}Attack\\ Cost(ms)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Clean\\ Videos\end{tabular} & \begin{tabular}[c]{@{}c@{}}Perturbed\\ Videos\end{tabular} & \begin{tabular}[c]{@{}c@{}}Drop\\ Rate\end{tabular} \\ \midrule
CSA & SiamRPN & AlexNet & 4720 & 0.851 & 0.458 & 46\% \\
FAN & SiamFC & AlexNet & 10 & 0.720 & 0.180 & 75\% \\
TTP & SiamRPN++ & ResNet-50 & 8 & 0.910 & 0.080 & 91\% \\
\midrule
Ours & SiamFC++ & GoogLeNet & 0 & 0.861 & 0.048 & 94\% \\ \bottomrule
\end{tabular}%
%}
\caption{Precision score relative to the real trajectory on OTB2015.}
\label{tab:untargeted}
\end{table}
